\bf Visualising How Non-linear Dimension Reduction Warps Your Data

### 2024-03-26 paper.qmd
Added bechmark value to remove long edge section

hex_full_count_df_loop2 <- hex_grid_with_counts |>
  dplyr::mutate(type = if_else(std_counts <= 0.1, "low", "high"))

@@

p2_n_rm_correct <-  ggplot(data = hex_full_count_df_loop2, aes(x = x, y = y)) +
  geom_polygon(color = "black", aes(group = hex_poly_id, fill = std_counts)) +
  geom_text(data = df_bin_centroids_low |> dplyr::filter(hexID %in% identify_rm_bins), color = "red", aes(x = c_x, y = c_y, group = hexID, label = "X"), size = 0.5) +
  #geom_point(data = UMAP_data, aes(x = UMAP1, y = UMAP2), alpha = 0.5) +
  scale_fill_viridis_c(direction = -1, na.value = "#ffffff", option = "C") +
  #coord_cartesian(xlim =c(-5, 7), ylim = c(-10, 10)) +
  theme_void() +
  theme(legend.position="none", legend.direction="horizontal", plot.title = element_text(size = 7, hjust = 0.5, vjust = -0.5),
        axis.title.x = element_blank(), axis.title.y = element_blank(),
        axis.text.x = element_blank(), axis.ticks.x = element_blank(),
        axis.text.y = element_blank(), axis.ticks.y = element_blank(),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(), #change legend key width
        legend.title = element_text(size=8), #change legend title font size
        legend.text = element_text(size=6)) +
  guides(fill = guide_colourbar(title = "Standardized count")) #+
  #annotate(geom = 'text', label = "b", x = -Inf, y = Inf, hjust = -0.3, vjust = 1, size = 3)

@@

#### Benchmark value to remove long edges

Achieving a smooth representation in 2D space is crucial, and one factor influencing this smoothness is the presence of long edges (see @fig-modelScurvermlgimp). These long edges occur when a line connects points that are distant in the triangular mesh, impacting the overall smoothness of the mesh.

To investigate the effect of removing long edges on the MSE, we analyzed the MSE for various benchmark values. Surprisingly, the results indicated that the MSE remained consistent across different benchmark values, as shown in @fig-diagnosticpltScurvelgrm. It's important to note that edges are defined only in the 2D model and do not extend to higher dimensions. Consequently, removing edges does not affect the model in higher dimensions.

There is no definitive rule for determining the benchmark value to remove long edges. However, we have a method to find a default value (see Appendix). Adjusting values around this default can help to find benchmark value to remove long edges, contributing to the construction of a smoother 2D representation (see @fig-diagnosticpltScurvelgrm).

The following steps will help to find a suitable value to remove long edges:

1. Plot the distribution of the 2D distances

```{r}
#| echo: false
#| fig-cap: "Distribution of 2D Euclidean distances."
#| label: fig-distScurve
#| fig-pos: H

@@

2. Find a value which is greater than smallest value

@@

<!--The removal of long edges is a critical step to create a smoother representation  by iteratively eliminating hexagons with excessive distances between centroids. This process eliminates outliers and noise while preserving essential local relationships within the data. To achieve this, distances between vertices are sorted, and unique distance values are extracted. By setting a threshold based on the largest difference between consecutive distance values, long edges are identified and removed. This refinement step contributes to enhancing the quality of the triangular mesh, ensuring a more accurate representation of the data structure.-->
<!--
```{r}
#| warning: false
#| echo: false
#| eval: false

## Import data

UMAP_s_curve <- read_rds("data/s_curve/s_curve_umap.rds")

num_bins_umap_s_curve <- 8
shape_val_umap_s_curve <- calculate_effective_shape_value(.data = UMAP_s_curve,
                                                          x = UMAP1, y = UMAP2) ## 1.259938
## To extract bin centroids
hexbin_data_object_umap_s_curve <- extract_hexbin_centroids(nldr_df = UMAP_s_curve, num_bins = num_bins_umap_s_curve, shape_val = shape_val_umap_s_curve, x = UMAP1, y = UMAP2)

df_bin_centroids_umap_s_curve <- hexbin_data_object_umap_s_curve$hexdf_data

UMAP_data_with_hb_id_s_curve <- UMAP_s_curve |>
  dplyr::mutate(hb_id = hexbin_data_object_umap_s_curve$hb_data@cID)

## To generate a data set with high-D and 2D training data
df_all_umap_s_curve <- dplyr::bind_cols(training_data |> dplyr::select(-ID), UMAP_data_with_hb_id_s_curve)

## Averaged on high-D
df_bin_umap_s_curve <- avg_highD_data(.data = df_all_umap_s_curve)

## Triangulate bin centroids
tr1_object_umap_s_curve <- triangulate_bin_centroids(df_bin_centroids_umap_s_curve, x, y)
tr_from_to_df_umap_s_curve <- generate_edge_info(triangular_object = tr1_object_umap_s_curve)

# ggplot(df_bin_centroids_umap_s_curve, aes(x = x, y = y)) +
#   geom_segment(data = tr_from_to_df_umap_s_curve, aes(x = x_from, y = y_from, xend = x_to, yend = y_to)) +
#   geom_point(size = 2, colour = "#33a02c") +
#   coord_equal()

## Compute 2D distances
distance_umap_s_curve <- cal_2d_dist(.data = tr_from_to_df_umap_s_curve)

distance_plot_s_curve <- plot_dist(distance_umap_s_curve) +
  #ggtitle("(b)" ) +
  ylab(expression(d^{(2)})) +
  theme(axis.text = element_text(size = 5),
        axis.title = element_text(size = 12))

## To find the benchmark value
benchmark_umap_s_curve <- find_benchmark_value(.data = distance_umap_s_curve, distance_col = distance)
benchmark_umap_s_curve <- 1.346694

# colour_long_edges(.data = distance_umap_s_curve, benchmark_value = benchmark_umap_s_curve,
#                   triangular_object = tr1_object_umap_s_curve, distance_col = distance)

trimesh_umap_s_curve <- ggplot(df_bin_centroids_umap_s_curve, aes(x = x, y = y)) +
  geom_segment(data = tr_from_to_df_umap_s_curve, aes(x = x_from, y = y_from, xend = x_to, yend = y_to)) +
  geom_point(size = 2, colour = "#33a02c") +
  coord_equal()

trimesh_umap_s_curve <- trimesh_umap_s_curve +
  #ggtitle("(a)") +
  xlab(expression(C[x]^{(2)})) + ylab(expression(C[y]^{(2)})) +
  theme_light() +
  theme(legend.position = "none", plot.title = element_text(size = 5, hjust = 0.5, vjust = -0.5),
        axis.title.x = element_blank(), axis.title.y = element_blank(),
        axis.text.x = element_blank(), axis.ticks.x = element_blank(),
        axis.text.y = element_blank(), axis.ticks.y = element_blank(),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank()#change legend key width
  ) +
  annotate(geom = 'text', label = 'a', x = -Inf, y = Inf, hjust = -0.5, vjust = 1.5, size = 3) 
# theme(axis.text = element_text(size = 5),
#       axis.title = element_text(size = 7))

trimesh_gr_umap_s_curve <- colour_long_edges(.data = distance_umap_s_curve, benchmark_value = benchmark_umap_s_curve, triangular_object = tr1_object_umap_s_curve, distance_col = distance)

trimesh_gr_umap_s_curve <- trimesh_gr_umap_s_curve +
  geom_point(size = 2, colour = "#33a02c") +
  #ggtitle("(b)") +
  xlab(expression(C[x]^{(2)})) + ylab(expression(C[y]^{(2)})) +
  theme_light() +
  #coord_equal() +
  theme(legend.position = "none", plot.title = element_text(size = 5, hjust = 0.5, vjust = -0.5),
        axis.title.x = element_blank(), axis.title.y = element_blank(),
        axis.text.x = element_blank(), axis.ticks.x = element_blank(),
        axis.text.y = element_blank(), axis.ticks.y = element_blank(),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank()#change legend key width
  ) +
  annotate(geom = 'text', label = 'b', x = -Inf, y = Inf, hjust = -0.5, vjust = 1.5, size = 3)

# ### Define type column
# df <- df_all_umap_s_curve |>
#   dplyr::select(tidyselect::starts_with("x")) |>
#   dplyr::mutate(type = "data") ## original dataset
# 
# df_b <- df_bin_umap_s_curve |>
#   dplyr::filter(hb_id %in% df_bin_centroids_umap_s_curve$hexID) |>
#   dplyr::select(-hb_id) |>
#   dplyr::mutate(type = "model") ## Data with summarized mean
# 
# df_exe <- dplyr::bind_rows(df_b, df)
# 
# distance_df_small_edges <- distance_umap_s_curve %>%
#   dplyr::filter(distance < benchmark_umap_s_curve)
# 
# distance_df_long_edges <- distance_umap_s_curve %>%
#   dplyr::filter(distance >= benchmark_umap_s_curve)
# 
# distance_df_edges <- dplyr::bind_rows(distance_df_small_edges, distance_df_long_edges)
# 
# langevitour::langevitour(df_exe[1:(length(df_exe)-1)], lineFrom = distance_df_edges$from , lineTo = distance_df_edges$to, group = df_exe$type, pointSize = 3, levelColors = c("#6a3d9a", "#33a02c"), lineColors = append(rep("black", length(distance_df_small_edges$from)), rep("red", length(distance_df_long_edges$from))))
#

```{r}
#| eval: false
#| warning: false
#| echo: false
#| label: fig-modelScurverdistcount
#| fig-cap: "plots to identify benchmark values"
##| out-width: 100%
#| fig-pos: H

cell_count_plot_s_curve + distance_plot_s_curve +
  #plot_annotation(tag_levels = 'a') +
  plot_layout(ncol = 2) &
  theme(legend.position='none', plot.tag = element_text(size = 8))
```

```{r}
#| eval: false
#| warning: false
#| echo: false
#| label: fig-modelScurvermlgimp
#| fig-cap: "What does the 2D model, constructed using UMAP (applied to the S-curve dataset), look like in high dimensions with long edges? (<https://youtu.be/pSL_G_n7-fM>) (a) 2D model without removing the long edges, and (b) 2D model with long edges coloured by red. The default benchmark value is used to identify long edges."
##| out-width: 100%
#| fig-pos: H

trimesh_umap_s_curve + trimesh_gr_umap_s_curve +
  #plot_annotation(tag_levels = 'a') +
  plot_layout(ncol = 2) &
  theme(legend.position='none', plot.tag = element_text(size = 8))
```
-->

@@

diff_start_df <- expand.grid(x_start = seq(min_x_start, max_x_start, by = 0.01), 
                             y_start = seq(min_y_start, max_y_start, by = 0.01))

@@

for (i in 1:23) { #NROW(diff_start_df)

@@

## If same total number of bins occurred only select ones with minimum error
### Obtain duplicate bins
dupli_bins <- mse_df |> 
  dplyr::count(num_non_empty_bins) |> 
  dplyr::filter(n > 1) |> 
  dplyr::pull(num_non_empty_bins)

### Group split by duplicated bins
duplicate_df_list <- mse_df |>
  dplyr::filter(num_non_empty_bins %in% dupli_bins) |>
  dplyr::arrange(num_non_empty_bins) |>
  dplyr::group_split(num_non_empty_bins)

  dd <- duplicate_df_list[[i]] |>
    dplyr::filter(mse == min(duplicate_df_list[[i]]$mse))

### Obtain the mse_df with not duplicated bins
not_dupli_df <- mse_df |>
  dplyr::filter(!(num_non_empty_bins %in% dupli_bins))

### Combine duplicated and not duplicated(corrected) bins dfs
mse_df <- dplyr::bind_rows(not_dupli_df, duplicate_df)

mse_plot <- ggplot(mse_df, aes(x = num_non_empty_bins,
                               y = mse
)) +
  geom_point() +
  geom_line() +
  # geom_vline(xintercept = 84, linetype="solid",
  #            color = "red", linewidth=0.8, alpha = 0.5) +
  theme_light() +
  theme(legend.position = "none", legend.title = element_blank(), plot.title = element_text(size = 7, hjust = 0.5, vjust = -0.5),
        axis.title = element_text(size = 7),
        axis.text = element_text(size = 7)) +
  #scale_colour_manual(values = c("#377eb8")) +
  ylab("MSE") +
  xlab("number of non-empty bins")

@@

```{r}
#| echo: false
#| fig-cap: "(a) Visualization of bin centroids and (b) hexagonal grid, showcasing the configuration before (colored in gray) and after (colored in light orange) shifting the starting point by an identical amount applied in both x and y directions, with a shift value of $0.537285$."
#| label: fig-scurveshifthexgridsexp
##| out-width: 100%
#| fig-pos: H

@@

```{r}
#| echo: false
#| fig-cap: "Hexbin plots shows the distribution of points before and after shifting the starting point of the hexagonal grid generated for UMAP applied to the training S-curve dataset. (a) Hexbin plot before shifting, and (b) Hexbin plot after shifting (identical shift applied in both x and y directions, with a shift value of $0.537285$)."
#| label: fig-scurveshifthexgrids
##| out-width: 100%
#| fig-pos: H

@@

```{r}
#| echo: false
#| fig-cap: "Absolute error from UMAP and tSNE applied to training PBMC3k dataset with diffferent parameter choices. What is the best parameter choice to create the model? The residual plot have a steep slope at the beginning, indicating that a smaller number of non-empty bins causes a larger amount of error. Then, the slope gradually declines or level off, indicating that a higher number of non-empty bins generates a smaller error. Using the elbow method, it was observed that when the number of non-empty bins is set to 439, the lowest error occurred with the parameters perplexity: 51."
#| label: fig-abserrorPBMC
#| fig-pos: H
#| out-width: 100%

>>>>

hex_full_count_df_loop2 <- hex_grid_with_counts |>
  dplyr::mutate(type = if_else(std_counts <= 0.2, "low", "high"))

@@

rm_centroid_df <- df_bin_centroids_low |> 
  dplyr::filter(hexID %in% identify_rm_bins)

p2_n_rm_correct <- ggplot(data = hex_full_count_df_loop2, aes(x = x, y = y)) +
  geom_polygon(color = "black", aes(group = hex_poly_id, fill = std_counts)) +
  geom_text(data = rm_centroid_df, color = "red", aes(x = c_x, y = c_y, group = hexID, label = "X"), size = 0.5) +
  #geom_point(data = UMAP_data, aes(x = UMAP1, y = UMAP2), alpha = 0.5) +
  scale_fill_viridis_c(direction = -1, na.value = "#ffffff", option = "C") +
  #coord_cartesian(xlim =c(-5, 7), ylim = c(-10, 10)) +
  theme_void() +
  theme(legend.position="none", legend.direction="horizontal", plot.title = element_text(size = 7, hjust = 0.5, vjust = -0.5),
        axis.title.x = element_blank(), axis.title.y = element_blank(),
        axis.text.x = element_blank(), axis.ticks.x = element_blank(),
        axis.text.y = element_blank(), axis.ticks.y = element_blank(),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(), #change legend key width
        legend.title = element_text(size=8), #change legend title font size
        legend.text = element_text(size=6)) +
  guides(fill = guide_colourbar(title = "Standardized count")) #+
  #annotate(geom = 'text', label = "b", x = -Inf, y = Inf, hjust = -0.3, vjust = 1, size = 3)

@@

#### Benchmark value for removing long edges

Creating a smooth 2D representation (see @fig-modelScurve (c)) requires removing edges that connect distant bin centroids within the triangular mesh (see @fig-modelScurve (b)). These edges only exist in the 2D model and do not extend into higher dimensions, ensuring that their removal does not impact the model in higher dimensions. While specific criteria for determining the benchmark value to remove long edges do not exist, the following steps provide an approach to identifying a suitable threshold:

1. Plot the distribution of the 2D Euclidean distances.
2. Identify the largest difference between consecutive distance values.
3. Take the largest distance value corresponding to this difference as the benchmark value.

```{r}
#| echo: false
#| fig-cap: "Distribution of 2D Euclidean distances between bin centroids of the triangular mesh generated with S-curve UMAP data."
#| label: fig-distScurve
#| fig-pos: H

@@

@@

@@

diff_start_df <- expand.grid(x_start = seq(min_x_start, max_x_start, length.out = 10), 
                             y_start = seq(min_y_start, max_y_start, length.out = 10)) |>
  add_row(x_start = min(umap_s_curve_scaled[["UMAP1"]]) - (sqrt(3) * hex_size_s_curve/2),
          y_start = min(umap_s_curve_scaled[["UMAP2"]]) - (1.5 * hex_size_s_curve/2))

@@

diff_start_df <- diff_start_df[c(1:5, 11:15,21:25, 101),]

for (i in 1:NROW(diff_start_df)) { #NROW(diff_start_df)

@@

# ## If same total number of bins occurred only select ones with minimum error
# ### Obtain duplicate bins
# dupli_bins <- mse_df |> 
#   dplyr::count(num_non_empty_bins) |> 
#   dplyr::filter(n > 1) |> 
#   dplyr::pull(num_non_empty_bins)
# 
# ### Group split by duplicated bins
# duplicate_df_list <- mse_df |>
#   dplyr::filter(num_non_empty_bins %in% dupli_bins) |>
#   dplyr::arrange(num_non_empty_bins) |>
#   dplyr::group_split(num_non_empty_bins)
# 
# ### Obtain one row from duplicates which have lowest error and hexsize
# duplicate_df <- data.frame(matrix(nrow = 0, ncol = 0))
# 
# for (i in 1:length(duplicate_df_list)) {
#   
#   dd <- duplicate_df_list[[i]] |>
#     dplyr::filter(mse == min(duplicate_df_list[[i]]$mse)) 
#   
#   duplicate_df <- dplyr::bind_rows(duplicate_df, dd)
#   
# }
# 
# ### Obtain the mse_df with not duplicated bins
# not_dupli_df <- mse_df |>
#   dplyr::filter(!(num_non_empty_bins %in% dupli_bins))
# 
# ### Combine duplicated and not duplicated(corrected) bins dfs
# mse_df <- dplyr::bind_rows(not_dupli_df, duplicate_df)

mse_plot_start_point <- ggplot(mse_df, aes(x = x_start,
                               y = y_start, colour = mse
)) +
  geom_point() +
  #geom_line() +
  # geom_vline(xintercept = 84, linetype="solid",
  #            color = "red", linewidth=0.8, alpha = 0.5) +
  theme_light() +
  theme(legend.title = element_blank(), plot.title = element_text(size = 7, hjust = 0.5, vjust = -0.5),
        axis.title = element_text(size = 7),
        axis.text = element_text(size = 7)) +
  viridis::scale_color_viridis(option = "D") +
  labs(x = "x start", y = "y start", color = "MSE") 
```

```{r}
#| echo: false
#| warning: false
#| fig-cap: "Goodness of fit statistics from UMAP applied to training S-curve dataset with different benchmark values to remove the low-density heaxgons. What is the effective benchmark value to remove the low-density heaxgons? The MSE plot have a steep slope at the beginning, indicating that a smaller benchmark causes a small amount of error. Then, the slope gradually increases or level up, indicating that a higher number of benchmark values generates a higher error. Using the reverse elbow method, when the benchmark value is set to 0.2, the slope of the Mean Squared Error (MSE) plot experiences a sudden and noticeable change, resembling an elbow-like shape. This point indicates that higher benchmark values remove the necessary bins as well which lead to distruct the 2D structure."
#| label: fig-mseScurvestartpoint
#| fig-pos: H

mse_plot_start_point
```

@@

```{r}
#| echo: false
#| fig-cap: "(a) Visualization of bin centroids and (b) hexagonal grid, showcasing the configuration before (colored in gray) and after (colored in light orange) shifting the starting point by an identical amount applied in both x and y directions, with a shift value of $0.537285$."
#| label: fig-scurveshifthexgridsexp
#| fig-pos: H

@@

```{r}
#| echo: false
#| fig-cap: "Hexbin plots shows the distribution of points before and after shifting the starting point of the hexagonal grid generated for UMAP applied to the training S-curve dataset. (a) Hexbin plot before shifting, and (b) Hexbin plot after shifting (identical shift applied in both x and y directions, with a shift value of $0.537285$)."
#| label: fig-scurveshifthexgrids
#| fig-pos: H

@@

```{r}
#| echo: false
#| fig-cap: "Absolute error from UMAP and tSNE applied to training PBMC3k dataset with diffferent parameter choices. What is the best parameter choice to create the model? The residual plot have a steep slope at the beginning, indicating that a smaller number of non-empty bins causes a larger amount of error. Then, the slope gradually declines or level off, indicating that a higher number of non-empty bins generates a smaller error. Using the elbow method, it was observed that when the number of non-empty bins is set to 439, the lowest error occurred with the parameters perplexity: 51."
#| label: fig-abserrorPBMC
#| fig-pos: H
#| out-width: 100%
#| out-height: 100%

### 2024-03-26 paper.tex
Added bechmark value to remove long edge section

\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[sharp corners, interior hidden, enhanced, borderline west={3pt}{0pt}{shadecolor}, breakable, boxrule=0pt, frame hidden]}{\end{tcolorbox}}\fi

@@

\hypertarget{benchmark-value-to-remove-long-edges}{%
\subsubsection{Benchmark value to remove long
edges}\label{benchmark-value-to-remove-long-edges}}

Achieving a smooth representation in 2D space is crucial, and one factor
influencing this smoothness is the presence of long edges (see
\textbf{?@fig-modelScurvermlgimp}). These long edges occur when a line
connects points that are distant in the triangular mesh, impacting the
overall smoothness of the mesh.

To investigate the effect of removing long edges on the MSE, we analyzed
the MSE for various benchmark values. Surprisingly, the results
indicated that the MSE remained consistent across different benchmark
values, as shown in \textbf{?@fig-diagnosticpltScurvelgrm}. It's
important to note that edges are defined only in the 2D model and do not
extend to higher dimensions. Consequently, removing edges does not
affect the model in higher dimensions.

There is no definitive rule for determining the benchmark value to
remove long edges. However, we have a method to find a default value
(see Appendix). Adjusting values around this default can help to find
benchmark value to remove long edges, contributing to the construction
of a smoother 2D representation (see
\textbf{?@fig-diagnosticpltScurvelgrm}).

The following steps will help to find a suitable value to remove long
edges:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Plot the distribution of the 2D distances
\end{enumerate}

@@

\caption{\label{fig-distScurve}Distribution of 2D Euclidean distances.}

@@

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{1}
\tightlist
\item
  Find a value which is greater than smallest value
\end{enumerate}

@@

\includegraphics{paper_files/figure-pdf/unnamed-chunk-36-1.pdf}

@@

{\centering \includegraphics[width=1\textwidth,height=\textheight]{paper_files/figure-pdf/fig-abserrorPBMC-1.pdf}

>>>>

\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[interior hidden, boxrule=0pt, borderline west={3pt}{0pt}{shadecolor}, enhanced, breakable, frame hidden, sharp corners]}{\end{tcolorbox}}\fi

@@

\hypertarget{benchmark-value-for-removing-long-edges}{%
\subsubsection{Benchmark value for removing long
edges}\label{benchmark-value-for-removing-long-edges}}

Creating a smooth 2D representation (see Figure~\ref{fig-modelScurve}
(c)) requires removing edges that connect distant bin centroids within
the triangular mesh (see Figure~\ref{fig-modelScurve} (b)). These edges
only exist in the 2D model and do not extend into higher dimensions,
ensuring that their removal does not impact the model in higher
dimensions. While specific criteria for determining the benchmark value
to remove long edges do not exist, the following steps provide an
approach to identifying a suitable threshold:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Plot the distribution of the 2D Euclidean distances.
\item
  Identify the largest difference between consecutive distance values.
\item
  Take the largest distance value corresponding to this difference as
  the benchmark value.
\end{enumerate}

@@

\caption{\label{fig-distScurve}Distribution of 2D Euclidean distances
between bin centroids of the triangular mesh generated with S-curve UMAP
data.}

@@

@@

{\centering \includegraphics{paper_files/figure-pdf/fig-mseScurvestartpoint-1.pdf}

\caption{\label{fig-mseScurvestartpoint}Goodness of fit statistics from
UMAP applied to training S-curve dataset with different benchmark values
to remove the low-density heaxgons. What is the effective benchmark
value to remove the low-density heaxgons? The MSE plot have a steep
slope at the beginning, indicating that a smaller benchmark causes a
small amount of error. Then, the slope gradually increases or level up,
indicating that a higher number of benchmark values generates a higher
error. Using the reverse elbow method, when the benchmark value is set
to 0.2, the slope of the Mean Squared Error (MSE) plot experiences a
sudden and noticeable change, resembling an elbow-like shape. This point
indicates that higher benchmark values remove the necessary bins as well
which lead to distruct the 2D structure.}

@@

{\centering \includegraphics[width=1\textwidth,height=1\textheight]{paper_files/figure-pdf/fig-abserrorPBMC-1.pdf}
